Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-15 paper.tex
Minor change in AoU text

For this study, we applied the bio2zarr compression to the chromosome 20 exome-like 
data from the All of Us dataset. The exome-like data is constructed by extracting from the WGS 
the SNP and indel variants that lie within the chromosome 20 exon regions of the Gencode v42 basic 
transcripts for all samples. This dataset, stored as a compressed VCF file of 7.44 GiB, 
includes 715,256 variants, of which 746 are classified as pathogenic or likely pathogenic.

>>>>

For this study, we applied the bio2zarr compression to the chromosome 20 exome-like 
data from the All of Us dataset. The exome-like data is constructed by extracting from all WGS samples
the SNP and indel variants that lie within the chromosome 20 exon regions of the Gencode v42 basic 
transcripts. This dataset, stored as a compressed VCF file of 7.44 GiB, 
includes 715,256 variants, of which 746 are classified as pathogenic or likely pathogenic.
